\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{File Transfer Protocol}
\author{Do Tuan Dung BI12-104}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This Python code utilizes a functional approach rather than a traditional MapReduce framework. Here's an explanation of how it achieves file searching without a Mapper and Reducer

\section{Functionality:}
Function Definition: The code defines a function find_files_with_extension that takes two arguments:
\\\ +)extension: The file extension to search for (e.g., "txt", "jpg").
\\\ +)search_path (optional): The    directory path to search in (defaults to the current directory).
\\\ +)File Path Generation: The function uses the glob module's glob.glob function to generate file paths. It constructs a pattern string f"{search_path}/*.{extension}" which expands to "path/.extension" (e.g., "C:/data/.txt").
\\\ +)Search and Store: The glob.glob function searches for files matching the pattern in the specified directory and returns a list of matching file paths. This list is stored in the found_file_paths variable.
\\\ +)User Input: The code prompts the user for the extension and search path (optional).
\\\ +)File Listing:
If found_file_paths is not empty (meaning files were found), the script iterates through the list and prints each file path.
If no files are found, it displays a message indicating no matches.
\subsection{The Longest Path:}
 Here is the "lgp.py" file:
\begin{verbatim}
import glob

def find_files_with_extension(extension, search_path="."):
  """
  This function searches for files with a specific extension in the given path.
  """
  found_file_paths = []
  for file in glob.glob(f"{search_path}/*.{extension}"):
    found_file_paths.append(file)
  return found_file_paths

extension_to_find = input("Enter the file extension to find (e.g., txt, jpg): ")
search_path = input("Enter the search path (leave blank for current directory): ") or "."

found_file_paths = find_files_with_extension(extension_to_find, search_path)

if found_file_paths:
  print("File(s) found:")
  for file_path in found_file_paths:
    print(file_path)
else:
  print("No file(s) found with the specified extension.")



\end{verbatim}
\end{document}

